Bayesian Hierarchical Modeling: An Introduction and Reassessment

### 2022-08-17 manuscript.Rmd
Add links to manuscript

  This paper is written in R Markdown. The R Markdown file, other R code, and additional information on this study can be found in the Online Supplement.

@@

# Model Specification 
In the following section, we specify two models that can be used for our application example: a normal and a log-normal model.^[Online Supplement A provides the parameterization for models of aggregated and individual data, to illustrate the difference with hierarchical models. ] We are aware that many psychologists do not engage with equations on a daily basis. In this section, however, we try to accessibly summarize the key considerations of model specification. We encourage everyone to read on and not skip the section. Additionally, we provide a non-technical verbal summary.

@@

## Fear of Commitment  
In many cases substantive researchers fear committing to prior settings because they are unsure about their choices for the type and settings of the distribution. Therefore, they tend to choose wide priors to indicate little prior knowledge about the parameter values [@aczel2018expert]. These include default priors offered by programming packages, such as `rstan` (Stan Development Team, 2019a; illustrated in Online Supplement B) and `brms` [@R-brms_a; @R-brms_b]. Wide priors are priors that allocate (approximately) equal probability density to a great range of values, such as a uniform distribution without bounds [@gelman2006prior]. However, wide priors can be problematic. First, since the distribution is spread out across a wide range of values, the probability density on any specific parameter value is very low. Therefore, any effect is unlikely under the prior as a wide range of effects is deemed plausible. This influences model comparisons: the support for the null hypothesis becomes increasingly large. This is also referred to as the Jeffreys-Lindley paradox [@lindley1957statistical].

@@

\begin{equation}
\begin{aligned}
\mu_{\gamma} &\sim \text{Student's t}(3, 1, 10), (\#eq:chosenpriors1) \\ 
\mu_{\beta}, \mu_{\delta} &\sim \text{Normal}(0, 1), \\ 
\sigma, \sigma_{\gamma}, \sigma_{\beta}, \sigma_{\delta} &\sim \text{Truncated-Student's t}_{+}(3, 0, 10). 
\end{aligned}
\end{equation}
The prior distributions `brms` specifies on the standard deviations can be transformed to prior distributions on variances. Prior distributions on variances have a smaller scale than priors on standard deviation. Note, however, that the transformation of the prior distributions is not as simple as the transformation of the parameter itself. In our Online Supplement, we provide R-code with a numeric solution to the transformation. For the `brms` priors, we obtain the following implied prior distributions on variances:

@@

We will continue with step 3 of the prior specification process and check what the expected data would look like according to the selected priors. The results of the prior prediction for the symbolic distance effect with the priors from Equation \@ref(eq:chosenpriors1) with the number of participants $n = 10$, the number of trials per condition $k = 60$, and the number of simulations $m = 1000$ are shown in panel A of Figure \@ref(fig:priorpredfigurepanel). Code for the simulations can be found in our Online Supplement.

@@

## Software 
There are many different programs available to fit Bayesian hierarchical models, that is, to obtain samples from the joint posterior distribution of parameters. In this tutorial, we focus on two of the most commonly used `R` packages, `rstan` [@R-rstan] and `brms` [@R-brms_a; @R-brms_b]. We assume that readers are somewhat familiar with `R`. The package `rstan` provides the most modern algorithms and flexibility in model set-up. The package `brms` was created as an overlay to `rstan` and is based on the well-known `lme4` syntax [@R-lme4]. The goal of `brms` is to ease the transition to Bayesian hierarchical modeling for novice users of Bayesian statistics. The packages work similarly for the normal and log-normal model. In this section, we explain how a model can be fitted in each package using code snippets. In addition, we offer a separate Rmarkdown file for each package in our Online Supplement that explains in more depth how to analyze the full symbolic distance effect model with the specific package.

@@

`Rstan` allows the application of `Stan` [@carpenter2017stan], a probabilistic programming language, in `R`. The package uses a version of the Hamiltonian Monte Carlo (HMC) algorithm, No-U-turn sampler [NUTS; Hoffman & Gelman, -@hoffman2014no], for sampling. `Rstan` requires two files: a `.stan` file containing the model specification and an R script containing the code for the model fitting. In the `.stan` file, the parameters, priors, and the likelihood are specified. An example `.stan` file of a simple, non-hierarchical normal model, where the variance is already known and the mean has to be estimated, is shown below [adapted example from @nicenboim2021introduction, Chapter 10]. The `.stan` file for the symbolic distance effect, including explanations, can be found in the Online Supplement. The file is divided into three sections: `data`, `parameters`, and `model`.

@@

The package `rstan` offers a lot of flexibility. It is possible to specify the likelihood and priors in the exact way as is wished. However, this comes with the price of some technical knowledge. The commented code for fitting the full symbolic distance effect model using `rstan`, can be found in [Online Supplement C: *Bayesian Hierarchical Modeling in Rstan*](https://www.dropbox.com/s/06f6vubmnhnm326/Appendix-C--Fit-BHM-in-rstan.pdf?dl=0).

@@

\normalsize If you do not specify a prior for a certain parameter, the default prior as explained in the prior section will be applied. It is possible to save all priors in an R `data.frame` and provide these in the `brm` function, this and the full code with explanation for fitting the full symbolic distance effect model using `brms` is shown in our [Online Supplement D: *Bayesian Hierarchical Modeling in brms*](https://www.dropbox.com/s/mthphl3ce2kk0xx/Appendix-D--Fit-BHM-in-brms.pdf?dl=0).^[In our example of the digit classification task we are applying a truncated normal prior distribution for only one parameter. This requires a slightly different `brms` formula and prior specification, explained in the Online Supplement.]

@@

When inspecting the trace plots of the symbolic distance effect parameters in the normal model, the posterior distributions of the parameters appear to have converged as the iterations come together and look similar to a caterpillar. The trace plot of one of the parameters, $\delta_{6, i}$, is shown in panel A for `rstan` and panel B for `brms` of Figure \@ref(fig:traceplots3p). The trace plot in panel B shows less overlap in the middle, indicating that `brms` had a bit more dependency within chains. This might be a sign of slight issues. However, not that much to be too concerned. Trace plots for other parameters can be found in the Online Supplement.

@@

The posterior distributions for the focal parameters in the normal model are presented in Figure \@ref(fig:modelposteriorsmufigure3). The posterior means estimated by `rstan` and `brms` can be found in the Online Supplement. The credible interval displayed in the figure is the Bayesian version of a confidence interval and provides a measure of uncertainty about the parameter value [@wagenmakers2018bayesian].

@@

fitrstanhiertable32 <- add_column(fitrstanhiertable22, Parameters = rownamesfitrstanhiertable2, .before = "Mean")
apa_table(fitrstanhiertable32, row.names = FALSE, caption = "Posterior Variance, Lower and Upper Bound of the 95\\% Credible Interval, Number of Effective Samples, and $\\hat{R}$ of the Variance Parameters as estimated by Rstan.", align = c("l", "c", "c", "c", "c", "c"), digits = 3, placement = "h", escape = FALSE)
```
Thanks to the hierarchical structure of the model, we can investigate whether the general effects hold for all the individuals by inspecting the individual variation and the individual parameter estimates. The individual variation is represented by the variance or standard deviation parameters in the model. The summaries of the posterior distributions of the variance parameters as estimated by `rstan` are shown in Table \@ref(tab:inddevtable). The estimates for the standard deviations by `brms` are smaller compared to `rstan` and can be found in Online Supplement D and H.

@@

Figure \@ref(fig:randomparfigure) shows the posterior means and 95% credible intervals for the individual effects of all 52 participants. Estimates are printed in increasing order, from lowest to highest. Pink intervals indicate that the 95% credible interval contains zero, while blue intervals are either entirely above or below zero. A corresponding figure with individual effect estimates for `brms` can be found in Online Supplement D.

@@

### Model Diagnostics 
Before interpreting the results, we have to check if the posterior distributions of the parameters have converged. The trace plot of $\mu_{\delta_{6}}$ is shown panel A for `rstan` and B for `brms` of Figure \@ref(fig:traceplotlog). Trace plots for all other parameters can be found in Online Supplement G. All plots look like a hairy caterpillar. Therefore, they indicate that the posterior distributions of the parameters have converged. $\hat{R}$ values shown in Figure \@ref(fig:traceplotlog)C for all parameters are all close to 1 and most of the number of effective samples shown in Figure \@ref(fig:traceplotlog)D exceed the total number of iterations. The number of effective samples for the general effects are comparatively low but still sufficient. In combination with the other diagnostics, we conclude that the posterior distributions of the parameters have converged and we proceed with the interpretation of the results.

@@

#### Individual effects 
Next, we inspect the individual deviations from the general effects. Table \@ref(tab:inddevtablelog) presents the estimates of the variance parameters by `rstan`. Results for brms can be found in Online Supplement H. 
```{r inddevtablelog, results = "asis", cache = TRUE}
# example - with SE 
# rstanfithier8log <- readRDS(file = "R objects/hier_logmodelc_adj.rds")
fitrstanhiertable2log <- summary(rstanfithier8log, pars = c("g", "g2", "g3", "g4", "g5", "g6"))$summary[,c("mean", "se_mean", "2.5%", "97.5%", "n_eff", "Rhat")]
# as.data.frame(fitrstanhiertable)
fitrstanhiertable2log2 <- as.data.frame(fitrstanhiertable2log)
rownamesfitrstanhiertable2log2 <-  c("$\\sigma_{\\gamma}^2$","$\\sigma_{\\beta}^2$", "$\\sigma_{\\delta_{7}}^2$", "$\\sigma_{\\delta_{6}}^2$", "$\\sigma_{\\delta_{4}}^2$", "$\\sigma_{\\delta_{3}}^2$")
colnames(fitrstanhiertable2log2) <- c("Mean", "SE", "Lower Bound", "Upper Bound", "$n_{eff}$","$\\hat{R}$")

@@

fitrstanhiertable32log <- add_column(fitrstanhiertable2log2, Parameters = rownamesfitrstanhiertable2log2, .before = "Mean")
apa_table(fitrstanhiertable32log, row.names = FALSE, caption = "Posterior Variance, Lower and Upper Bound of the 95\\% Credible Interval, the Number of Effective Samples, and the $\\hat{R}$ of the Variance Parameters as estimated by Rstan.", align = c("l", "c", "c", "c", "c", "c"), digits = 3, placement = "h", escape = FALSE)
```
The estimated parameter values for the variance terms are very small, but different from zero. This indicates that individuals may vary slightly with respect to the general effect parameters. The estimates for the standard deviations by `brms` are similar compared to the estimates by `rstan`, but slightly smaller. The exact estimates by `brms` can be found in Online Supplement F and H.
Figure \@ref(fig:randomparplotlog) shows the individual estimates for the digit and side effects. The pink lines indicate that the 95% credible interval of the individual effect contains zero. The estimated general effect is represented by the dashed line. For $\beta$, $\delta_{7}$, and $\delta_{3}$, most 95% credible intervals contain zero. For $\delta_{6}$ and $\delta_{4}$, most credible intervals are entirely larger than zero, indicating an increase in RT for most participants.

@@

First, we kept the discussion of the software packages and code fairly brief. We provide further code examples for the digit classification task in the Online Supplement. For different models, it may be useful to study additional tutorials and books. For `rstan`, we recommend the `Stan` manual [@stan2018a; @stan2018b]. For `brms` there are several useful tutorials [@R-brms_a; @R-brms_b; @burkner2019ordinal]. There are also several resources for Bayesian estimation with other samplers [@lee2013bayesian; @rouder2013hierarchical]. Two other useful tutorials for Bayesian modeling are Schad, Betancourt, and
Vasishth [-@schad2019toward] and Schad, Nicenboim, Bürkner, Betancourt, and Vasishth [-@schad2021workflow].

>>>>

  This paper is written in R Markdown. The R Markdown file, other R code, and additional information on this study can be found in the [Online Supplement](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment).

@@

# Model Specification 
In the following section, we specify two models that can be used for our application example: a normal and a log-normal model.^[[Online Supplement A](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment/blob/main/A%20-%20Model%20Parameterization%20/Online-Supplement-A---Model-Parameterization-for-Aggregated-and-Individual-Models.pdf) provides the parameterization for models of aggregated and individual data, to illustrate the difference with hierarchical models. ] We are aware that many psychologists do not engage with equations on a daily basis. In this section, however, we try to accessibly summarize the key considerations of model specification. We encourage everyone to read on and not skip the section. Additionally, we provide a non-technical verbal summary.

@@

## Fear of Commitment  
In many cases substantive researchers fear committing to prior settings because they are unsure about their choices for the type and settings of the distribution. Therefore, they tend to choose wide priors to indicate little prior knowledge about the parameter values [@aczel2018expert]. These include default priors offered by programming packages, such as `rstan` (Stan Development Team, 2019a; illustrated in [Online Supplement B](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment/blob/main/B%20-%20Default%20Priors%20Rstan/Online-Supplement-B---Default-Priors-Rstan.pdf)) and `brms` [@R-brms_a; @R-brms_b]. Wide priors are priors that allocate (approximately) equal probability density to a great range of values, such as a uniform distribution without bounds [@gelman2006prior]. However, wide priors can be problematic. First, since the distribution is spread out across a wide range of values, the probability density on any specific parameter value is very low. Therefore, any effect is unlikely under the prior as a wide range of effects is deemed plausible. This influences model comparisons: the support for the null hypothesis becomes increasingly large. This is also referred to as the Jeffreys-Lindley paradox [@lindley1957statistical].

@@

\begin{equation}
\begin{aligned}
\mu_{\gamma} &\sim \text{Student's t}(3, 1, 10), (\#eq:chosenpriors1) \\ 
\mu_{\beta}, \mu_{\delta} &\sim \text{Normal}(0, 1), \\ 
\sigma, \sigma_{\gamma}, \sigma_{\beta}, \sigma_{\delta} &\sim \text{Truncated-Student's t}_{+}(3, 0, 10). 
\end{aligned}
\end{equation}
The prior distributions `brms` specifies on the standard deviations can be transformed to prior distributions on variances. Prior distributions on variances have a smaller scale than priors on standard deviation. Note, however, that the transformation of the prior distributions is not as simple as the transformation of the parameter itself. In our [Online Supplement](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment/tree/main/R%20code/Prior%20transformation), we provide R-code with a numeric solution to the transformation. For the `brms` priors, we obtain the following implied prior distributions on variances:

@@

We will continue with step 3 of the prior specification process and check what the expected data would look like according to the selected priors. The results of the prior prediction for the symbolic distance effect with the priors from Equation \@ref(eq:chosenpriors1) with the number of participants $n = 10$, the number of trials per condition $k = 60$, and the number of simulations $m = 1000$ are shown in panel A of Figure \@ref(fig:priorpredfigurepanel). Code for the simulations can be found in our [Online Supplement](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment).

@@

## Software 
There are many different programs available to fit Bayesian hierarchical models, that is, to obtain samples from the joint posterior distribution of parameters. In this tutorial, we focus on two of the most commonly used `R` packages, `rstan` [@R-rstan] and `brms` [@R-brms_a; @R-brms_b]. We assume that readers are somewhat familiar with `R`. The package `rstan` provides the most modern algorithms and flexibility in model set-up. The package `brms` was created as an overlay to `rstan` and is based on the well-known `lme4` syntax [@R-lme4]. The goal of `brms` is to ease the transition to Bayesian hierarchical modeling for novice users of Bayesian statistics. The packages work similarly for the normal and log-normal model. In this section, we explain how a model can be fitted in each package using code snippets. In addition, we offer a separate Rmarkdown file for each package in our [Online Supplement](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment) that explains in more depth how to analyze the full symbolic distance effect model with the specific package.

@@

`Rstan` allows the application of `Stan` [@carpenter2017stan], a probabilistic programming language, in `R`. The package uses a version of the Hamiltonian Monte Carlo (HMC) algorithm, No-U-turn sampler [NUTS; Hoffman & Gelman, -@hoffman2014no], for sampling. `Rstan` requires two files: a `.stan` file containing the model specification and an R script containing the code for the model fitting. In the `.stan` file, the parameters, priors, and the likelihood are specified. An example `.stan` file of a simple, non-hierarchical normal model, where the variance is already known and the mean has to be estimated, is shown below [adapted example from @nicenboim2021introduction, Chapter 10]. The `.stan` file for the symbolic distance effect, including explanations, can be found in the [Online Supplement](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment/blob/main/R%20objects/rstan/normal%20model/myModel.stan). The file is divided into three sections: `data`, `parameters`, and `model`.

@@

The package `rstan` offers a lot of flexibility. It is possible to specify the likelihood and priors in the exact way as is wished. However, this comes with the price of some technical knowledge. The commented code for fitting the full symbolic distance effect model using `rstan`, can be found in [Online Supplement C: *Bayesian Hierarchical Modeling in Rstan*](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment/blob/main/C%20-%20Tutorial%20Normal%20Model%20Rstan/Online-Supplement-C---Bayesian-Hierarchical-Modeling-in-rstan.pdf).

@@

\normalsize If you do not specify a prior for a certain parameter, the default prior as explained in the prior section will be applied. It is possible to save all priors in an R `data.frame` and provide these in the `brm` function, this and the full code with explanation for fitting the full symbolic distance effect model using `brms` is shown in our [Online Supplement D: *Bayesian Hierarchical Modeling in brms*](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment/blob/main/D%20-%20Tutorial%20Normal%20Model%20brms/Online-Supplement-D---Bayesian-Hierarchical-Modeling-in-brms.pdf).^[In our example of the digit classification task we are applying a truncated normal prior distribution for only one parameter. This requires a slightly different `brms` formula and prior specification, explained in the Online Supplement.]

@@

When inspecting the trace plots of the symbolic distance effect parameters in the normal model, the posterior distributions of the parameters appear to have converged as the iterations come together and look similar to a caterpillar. The trace plot of one of the parameters, $\delta_{6, i}$, is shown in panel A for `rstan` and panel B for `brms` of Figure \@ref(fig:traceplots3p). The trace plot in panel B shows less overlap in the middle, indicating that `brms` had a bit more dependency within chains. This might be a sign of slight issues. However, not that much to be too concerned. Trace plots for other parameters can be found in 
[Online Supplement G](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment/tree/main/G%20-%20Trace%20Plots%20).

@@

The posterior distributions for the focal parameters in the normal model are presented in Figure \@ref(fig:modelposteriorsmufigure3). The posterior means estimated by `rstan` and `brms` can be found in [Online Supplement H](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment/tree/main/H%20-%20Posterior%20Distributions%20Tables). The credible interval displayed in the figure is the Bayesian version of a confidence interval and provides a measure of uncertainty about the parameter value [@wagenmakers2018bayesian].

@@

fitrstanhiertable32 <- add_column(fitrstanhiertable22, Parameters = rownamesfitrstanhiertable2, .before = "Mean")
apa_table(fitrstanhiertable32, row.names = FALSE, caption = "Posterior Variance, Lower and Upper Bound of the 95\\% Credible Interval, Number of Effective Samples, and $\\hat{R}$ of the Variance Parameters as estimated by Rstan.", align = c("l", "c", "c", "c", "c", "c"), digits = 3, placement = "h", escape = FALSE)
```
Thanks to the hierarchical structure of the model, we can investigate whether the general effects hold for all the individuals by inspecting the individual variation and the individual parameter estimates. The individual variation is represented by the variance or standard deviation parameters in the model. The summaries of the posterior distributions of the variance parameters as estimated by `rstan` are shown in Table \@ref(tab:inddevtable). The estimates for the standard deviations by `brms` are smaller compared to `rstan` and can be found in [Online Supplements D and H](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment).

@@

Figure \@ref(fig:randomparfigure) shows the posterior means and 95% credible intervals for the individual effects of all 52 participants. Estimates are printed in increasing order, from lowest to highest. Pink intervals indicate that the 95% credible interval contains zero, while blue intervals are either entirely above or below zero. A corresponding figure with individual effect estimates for `brms` can be found in [Online Supplement D](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment/blob/main/D%20-%20Tutorial%20Normal%20Model%20brms/Online-Supplement-D---Bayesian-Hierarchical-Modeling-in-brms.pdf).

@@

### Model Diagnostics 
Before interpreting the results, we have to check if the posterior distributions of the parameters have converged. The trace plot of $\mu_{\delta_{6}}$ is shown panel A for `rstan` and B for `brms` of Figure \@ref(fig:traceplotlog). Trace plots for all other parameters can be found in [Online Supplement G](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment/tree/main/G%20-%20Trace%20Plots%20). All plots look like a hairy caterpillar. Therefore, they indicate that the posterior distributions of the parameters have converged. $\hat{R}$ values shown in Figure \@ref(fig:traceplotlog)C for all parameters are all close to 1 and most of the number of effective samples shown in Figure \@ref(fig:traceplotlog)D exceed the total number of iterations. The number of effective samples for the general effects are comparatively low but still sufficient. In combination with the other diagnostics, we conclude that the posterior distributions of the parameters have converged and we proceed with the interpretation of the results.

@@

#### Individual effects 
Next, we inspect the individual deviations from the general effects. Table \@ref(tab:inddevtablelog) presents the estimates of the variance parameters by `rstan`. Results for brms can be found in [Online Supplement H](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment/blob/main/H%20-%20Posterior%20Distributions%20Tables/Online-Supplement-H---Tables-with-Information-on-Posterior-Distributions.pdf). 
```{r inddevtablelog, results = "asis", cache = TRUE}
# example - with SE 
# rstanfithier8log <- readRDS(file = "R objects/hier_logmodelc_adj.rds")
fitrstanhiertable2log <- summary(rstanfithier8log, pars = c("g", "g2", "g3", "g4", "g5", "g6"))$summary[,c("mean", "se_mean", "2.5%", "97.5%", "n_eff", "Rhat")]
# as.data.frame(fitrstanhiertable)
fitrstanhiertable2log2 <- as.data.frame(fitrstanhiertable2log)
rownamesfitrstanhiertable2log2 <-  c("$\\sigma_{\\gamma}^2$","$\\sigma_{\\beta}^2$", "$\\sigma_{\\delta_{7}}^2$", "$\\sigma_{\\delta_{6}}^2$", "$\\sigma_{\\delta_{4}}^2$", "$\\sigma_{\\delta_{3}}^2$")
colnames(fitrstanhiertable2log2) <- c("Mean", "SE", "Lower Bound", "Upper Bound", "$n_{eff}$","$\\hat{R}$")

@@

fitrstanhiertable32log <- add_column(fitrstanhiertable2log2, Parameters = rownamesfitrstanhiertable2log2, .before = "Mean")
apa_table(fitrstanhiertable32log, row.names = FALSE, caption = "Posterior Variance, Lower and Upper Bound of the 95\\% Credible Interval, the Number of Effective Samples, and the $\\hat{R}$ of the Variance Parameters as estimated by Rstan.", align = c("l", "c", "c", "c", "c", "c"), digits = 3, placement = "h", escape = FALSE)
```
The estimated parameter values for the variance terms are very small, but different from zero. This indicates that individuals may vary slightly with respect to the general effect parameters. The estimates for the standard deviations by `brms` are similar compared to the estimates by `rstan`, but slightly smaller. The exact estimates by `brms` can be found in [Online Supplements F and H](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment).
Figure \@ref(fig:randomparplotlog) shows the individual estimates for the digit and side effects. The pink lines indicate that the 95% credible interval of the individual effect contains zero. The estimated general effect is represented by the dashed line. For $\beta$, $\delta_{7}$, and $\delta_{3}$, most 95% credible intervals contain zero. For $\delta_{6}$ and $\delta_{4}$, most credible intervals are entirely larger than zero, indicating an increase in RT for most participants.

@@

First, we kept the discussion of the software packages and code fairly brief. We provide further code examples for the digit classification task in the [Online Supplement](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment). For different models, it may be useful to study additional tutorials and books. For `rstan`, we recommend the `Stan` manual [@stan2018a; @stan2018b]. For `brms` there are several useful tutorials [@R-brms_a; @R-brms_b; @burkner2019ordinal]. There are also several resources for Bayesian estimation with other samplers [@lee2013bayesian; @rouder2013hierarchical]. Two other useful tutorials for Bayesian modeling are Schad, Betancourt, and
Vasishth [-@schad2019toward] and Schad, Nicenboim, Bürkner, Betancourt, and Vasishth [-@schad2021workflow].
